Supplementary Material for "Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-07-28 analysis/paper_draft4supp.Rmd
remove app folder, main R folder

---
title: Supplementary Material for "Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data"
date: "`r Sys.Date()`"
blinded: 0
authors:
- name: "[Sachin S. Pandya](https://orcid.org/0000-0001-7387-1307)"
  affiliation: University of Connecticut
  email: sachin.pandya@uconn.edu
- name: "Xiaomeng Li"
  affiliation: University of Connecticut
- name: "[Eric Barón](https://orcid.org/0000-0003-1934-1932)"
  affiliation: University of Connecticut
- name: "[Timothy E. Moore](https://orcid.org/0000-0002-9576-0517)"
  affiliation: University of Connecticut
output:
  bookdown::pdf_book: 
      base_format: rticles::asa_article
      citation_package: "default"
      keep_tex: TRUE
header-includes: 
  - \usepackage{amsmath}
  - \usepackage{subfig}
  - \newcommand{\beginsupplement}{
    \setcounter{table}{0}  
    \renewcommand{\thetable}{S\arabic{table}} 
    \setcounter{figure}{0} 
    \renewcommand{\thefigure}{S\arabic{figure}}
    }
#fontsize: 12pt
bibliography: references.bib
biblio-style: agsm.bst

>>>>

---
title: Supplementary Material for "Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data"
date: "`r Sys.Date()`"
blinded: 1
authors:
- name: "[Sachin S. Pandya](https://orcid.org/0000-0001-7387-1307)"
  affiliation: University of Connecticut
  email: sachin.pandya@uconn.edu
- name: "Xiaomeng Li"
  affiliation: University of Connecticut
- name: "[Eric Barón](https://orcid.org/0000-0003-1934-1932)"
  affiliation: University of Connecticut
- name: "[Timothy E. Moore](https://orcid.org/0000-0002-9576-0517)"
  affiliation: University of Connecticut
output:
  bookdown::pdf_book: 
      base_format: rticles::asa_article
      citation_package: "default"
      keep_tex: TRUE
header-includes: 
  - \usepackage{amsmath}
  - \usepackage{subfig}
  - \newcommand{\beginsupplement}{
    \setcounter{table}{0}  
    \renewcommand{\thetable}{S\arabic{table}} 
    \setcounter{figure}{0} 
    \renewcommand{\thefigure}{S\arabic{figure}}
    }
#fontsize: 12pt
bibliography: references.bib
biblio-style: agsm.bst
